Dendritic Ca2+ as a Predictor of Stimulus Perception and Behavior

### 2017-09-13 presentation_Naoya/demo.tex
asd

\section{Goal}
\begin{frame}[fragile]{Goal}
The goal of this project is to investigate the following:
\begin{itemize}
\only<+->{
\item What is the relationship between Ca2+ activity and stimulus intensity/behavior}
\only<+->{
\item Can we build predictive classifiers for this data?}
\only<+->{
\item Does a multivariate approach give us any significant advantage over a univariate one?}
\end{itemize}
\end{frame}

@@

\begin{frame}[fragile]{SVM - What is an SVM? The Margin}
\begin{columns}[T,onlytextwidth]
\column{0.4\textwidth}
\only<+->{
\begin{center}
\bigskip
\bigskip
\bigskip
The one that maximizes the hyperplanes' distance from the nearest datapoints of either class while classifying all data correctly - \textbf{the margin}
\end{center}}
\column{0.55\textwidth}
\begin{center}
\only<+->{
\begin{figure}
      \includegraphics[height=0.9\textwidth]{svm_mar.png}
	\end{figure}}
	%\only<+->{
	%\begin{figure}
    %  \includegraphics[height=0.3\textwidth]{svm_exp.png}
	%\end{figure}}
	\end{center}
\end{columns}
\end{frame}

\begin{frame}[fragile]{SVM - What is an SVM? The Margin}
\begin{columns}[T,onlytextwidth]
\column{0.4\textwidth}
\begin{center}
\only<+->{
The hyperplane is given by
\begin{align*}
g(\mathbf{x}) = \mathbf{w^Tx + b}
\end{align*}}
\only<+->{
It turns out that the margin is given by $\frac{2}{||w||}$ and we maximize it by minimizing
\begin{align*}
\frac{1}{2}||\mathbf{w}||_2^2
\end{align*}}
\only<+->{
under the constraint that \textbf{all data are classified correctly}.}
\end{center}
\column{0.55\textwidth}
\begin{center}
\begin{figure}
      \includegraphics[height=0.9\textwidth]{svm_mar.png}
	\end{figure}
	%\only<+->{
	%\begin{figure}
    %  \includegraphics[height=0.3\textwidth]{svm_exp.png}
	%\end{figure}}
	\end{center}
\end{columns}
\end{frame}

@@

\begin{frame}[fragile]{SVM - What is an SVM? Linearily Nonseparable/Noisy Data}
\only<+->{
We permit Errors, but still penalize them!}
\begin{columns}[T,onlytextwidth]
\column{0.5\textwidth}
\begin{center}
\only<+->{
\begin{figure}
      \includegraphics[height=0.8\textwidth]{svm_nonsep_mar.png}
	\end{figure}}
	%\only<+->{
	%\begin{figure}
    %  \includegraphics[height=0.3\textwidth]{svm_exp.png}
	%\end{figure}}
	\end{center}
\column{0.5\textwidth}
\begin{center}
\only<+->{
\begin{figure}
      \includegraphics[height=0.8\textwidth]{svm_nonsep_err.png}
	\end{figure}}
	%\only<+->{
	%\begin{figure}
    %  \includegraphics[height=0.3\textwidth]{svm_exp.png}
	%\end{figure}}
	\end{center}
\end{columns}
\end{frame}

\begin{frame}[fragile]{SVM - What is an SVM? Linearily Nonseparable/Noisy Data}
\begin{columns}[T,onlytextwidth]
\column{0.5\textwidth}
\only<+->{
Instead of $\frac{1}{2}||\mathbf{w}||_2^2$ we now minimize
\begin{align*}
\frac{1}{2}||\mathbf{w}||_2^2 + C\sum_{i=1}^n \xi_i}
\end{align*}
\only<+->{
where $\xi_i$ is the distance of a data point from their correct decision region.}

\only<+->{
\textbf{The parameter C lets us now control the tradeoff between the generalization and training error (overfitting).}}
\column{0.5\textwidth}
\begin{center}
\begin{figure}
      \includegraphics[height=0.8\textwidth]{svm_nonsep_err.png}
	\end{figure}
	%\only<+->{
	%\begin{figure}
    %  \includegraphics[height=0.3\textwidth]{svm_exp.png}
	%\end{figure}}
	\end{center}
\end{columns}
\end{frame}

\begin{frame}[fragile]{SVM Specifics}
\begin{itemize}
\only<+->{
\item All data are normalized to zero mean and unit variance}
\only<+->{
\item Crossvalidation is performed to conrol for overfitting}
\end{itemize}

@@

\begin{frame}[fragile]{Behavioral Prediction - Most Accurate Dendrites}
\begin{table}
    \caption*{Different dataset - Stimulus strength 1 (near thereshold)}
    \begin{tabular}{c|c|c}
      \toprule
      Dendrite \# & $\mu_{acc}$ & $\sigma_{acc}$\\
      \midrule
      88 & 0.80 & 0.08\\
      57 & 0.80 & 0.08\\
      92 & 0.78 & 0.06\\
      56 & 0.76 & 0.10\\
      \bottomrule
    \end{tabular}
  \end{table}
\end{frame}

@@

\begin{frame}
\begin{thebibliography}{9}
\bibitem {taka} Takahashi, N., Oertner, G. T., Hegemann, P. \& Larkum, E. M. Active cortical dendrites modulate perception. Science 335, 1587-1590 (2016)
\bibitem {mante} Mante V., Sussillo D., Shenoy KV., Newsome WT. Context-dependent computation by recurrent dynamics in prefrontal cortex. Nature 503, 78-84 (2013)
\bibitem {pinto} Pinto da Costa, J. New Results in Weighted Correlation and Weighted Principal Component Analysis with Applications, Chapter 2 (2015)
\end{thebibliography}
\end{frame}

>>>>

\section{Goal}
\begin{frame}[fragile]{Goal}
The goal of this project is to investigate the following:
\begin{itemize}
\only<+->{
\item What is the relationship between Ca2+ activity and stimulus intensity/behavior?}
\only<+->{
\item Can we build predictive classifiers for this data?}
\only<+->{
\item Does a multivariate approach give us any significant advantage over a univariate one?}
\end{itemize}
\end{frame}

@@

\begin{frame}[fragile]{SVM - What is an SVM? The Margin}
\begin{columns}[T,onlytextwidth]
\column{0.4\textwidth}
\only<+->{
\begin{center}
\bigskip
\bigskip
\bigskip
The one that maximizes the hyperplane's distance from the nearest datapoints of either class while classifying all data correctly - \textbf{the margin}
\end{center}}
\column{0.55\textwidth}
\begin{center}
\only<+->{
\begin{figure}
      \includegraphics[height=0.9\textwidth]{svm_mar.png}
	\end{figure}}
	%\only<+->{
	%\begin{figure}
    %  \includegraphics[height=0.3\textwidth]{svm_exp.png}
	%\end{figure}}
	\end{center}
\end{columns}
\end{frame}

\begin{frame}[fragile]{SVM - What is an SVM? The Margin}
\begin{columns}[T,onlytextwidth]
\column{0.4\textwidth}
\begin{center}
\only<+->{
Maximization of the margin can be formulated as a \textbf{constrained minimization problem}!

}
%\only<+->{
%The hyperplane is given by
%\begin{align*}
%g(\mathbf{x}) = \mathbf{w^Tx + b}
%\end{align*}}
%\only<+->{
%It turns out that the margin is given by $\frac{2}{||w||}$ and we maximize it by minimizing
%\begin{align*}
%\frac{1}{2}||\mathbf{w}||_2^2
%\end{align*}}
%\only<+->{
%\bigskip
%\bigskip
%With the constraint that \textbf{all data are classified correctly}.}
\end{center}
\column{0.55\textwidth}
\begin{center}
\begin{figure}
      \includegraphics[height=0.9\textwidth]{svm_mar.png}
	\end{figure}
	%\only<+->{
	%\begin{figure}
    %  \includegraphics[height=0.3\textwidth]{svm_exp.png}
	%\end{figure}}
	\end{center}
\end{columns}
\end{frame}

@@

\begin{frame}[fragile]{SVM - What is an SVM? Linearily Nonseparable/Noisy Data}
\only<+->{
We permit errors, but still penalize them!}
\begin{columns}[T,onlytextwidth]
\column{0.5\textwidth}
\begin{center}
\only<+->{
\begin{figure}
      \includegraphics[height=0.8\textwidth]{svm_nonsep_mar.png}
	\end{figure}}
	%\only<+->{
	%\begin{figure}
    %  \includegraphics[height=0.3\textwidth]{svm_exp.png}
	%\end{figure}}
	\end{center}
\column{0.5\textwidth}
\begin{center}
\only<+->{
\begin{figure}
      \includegraphics[height=0.8\textwidth]{svm_nonsep_err.png}
	\end{figure}}
	%\only<+->{
	%\begin{figure}
    %  \includegraphics[height=0.3\textwidth]{svm_exp.png}
	%\end{figure}}
	\end{center}
\end{columns}
\end{frame}

%\begin{frame}[fragile]{SVM - What is an SVM? Linearily Nonseparable/Noisy Data}
%\begin{columns}[T,onlytextwidth]
%\column{0.5\textwidth}
%\only<+->{
%Instead of $\frac{1}{2}||\mathbf{w}||_2^2$ we now minimize
%\begin{align*}
%\frac{1}{2}||\mathbf{w}||_2^2 + C\sum_{i=1}^n \xi_i}
%\end{align*}
%\only<+->{
%where $\xi_i$ is the distance of a data point from their correct decision region.}
%
%\only<+->{
%\textbf{The parameter C lets us now control the tradeoff between the generalization and training error (overfitting).}}
%\column{0.5\textwidth}
%\begin{center}
%\begin{figure}
%      \includegraphics[height=0.8\textwidth]{svm_nonsep_err.png}
%	\end{figure}
%	%\only<+->{
%	%\begin{figure}
%    %  \includegraphics[height=0.3\textwidth]{svm_exp.png}
%	%\end{figure}}
%	\end{center}
%\end{columns}
%\end{frame}

\begin{frame}[fragile]{SVM - What is an SVM? Linearily Nonseparable/Noisy Data}
\begin{columns}[T,onlytextwidth]
\column{0.5\textwidth}
\only<+->{
We can still formulate this as a constrained minimization problem, but now we \textbf{minimize the sum of errors while maximizing the margin}.}
\only<+->{

\bigskip
The coefficient $C$ controls the width of the margin at the expense of worse separation during training.}
\column{0.5\textwidth}
\begin{center}
\begin{figure}
      \includegraphics[height=0.8\textwidth]{svm_nonsep_err.png}
	\end{figure}
	%\only<+->{
	%\begin{figure}
    %  \includegraphics[height=0.3\textwidth]{svm_exp.png}
	%\end{figure}}
	\end{center}
\end{columns}
\end{frame}

\begin{frame}[fragile]{SVM Specifics}
\begin{itemize}
\only<+->{
\item All data are normalized to zero mean and unit variance}
\only<+->{
\item Crossvalidation is performed to control for overfitting}
\end{itemize}

@@

\begin{frame}[fragile]{Behavioral Prediction - Most Accurate Dendrites}
\begin{table}
    \caption*{Different dataset - Stimulus strength 1 (near threshold)}
    \begin{tabular}{c|c|c}
      \toprule
      Dendrite \# & $\mu_{acc}$ & $\sigma_{acc}$\\
      \midrule
      88 & 0.80 & 0.08\\
      57 & 0.80 & 0.08\\
      92 & 0.78 & 0.06\\
      56 & 0.76 & 0.10\\
      \bottomrule
    \end{tabular}
  \end{table}
\end{frame}

@@

\begin{frame}
\begin{thebibliography}{9}
\bibitem {taka} Takahashi, N., Oertner, G. T., Hegemann, P. \& Larkum, E. M. Active cortical dendrites modulate perception. Science 335, 1587-1590 (2016).
\bibitem {mante} Mante V., Sussillo D., Shenoy, K. V., Newsome, W. T. Context-dependent computation by recurrent dynamics in prefrontal cortex. Nature 503, 78-84 (2013).
\bibitem {pinto} Pinto da Costa, J. New Results in Weighted Correlation and Weighted Principal Component Analysis with Applications, Chapter 2 (2015).
\end{thebibliography}
\end{frame}
